Optimal Tetrahelices Transforming between the Boerdijk-Coxeter Helix and a Planar-faced Tetrahelix

### 2018-03-07 r1doc/TetrahelixUntwistV2.tex
added video and others

A BC helix does not rest stably on a plane. It is convenient to
be able to ``untwist'' it and to form a tetrahelix space frame that has a
flat planar surface. By making length changes in a certain way, we can
untwist a tetrahelix to form a \emph{tetrabeam} which has planar faces
and has, for example, an equilateral triangular profile. This paper
develops the equations needed to untwist the tetrahelix. All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix},
from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
are taken.

@@

Now that we have shown that axes are coincident and parallel and that the pitches
are the same for all helices, we can assert that any optimum tetrahelix can
be generated with an equation for helices:
\begin{equation}
\label{eq:triple}
\vec{V}_{triple}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_c \cos(n \alpha +  c 2 \pi /3 + \phi_c)$\\
   $ r_c \sin(n \alpha +  c 2 \pi /3 + \phi_c) $\\
   $ \frac{d(n +c / 3)}{3}   $
  \end{tabular}
  \right ],
\end{equation}
\text{where: \qquad}
\begin{tabular}{l}
  $c \in \{0,1,2\}$,
  \end{tabular}      
which would be much more complicated if the axes where not coincident.
\highlighttext{
Note that we have not yet shown that the relationships of the radius $r_c$ or
the phase $\phi_c$ for the three helices, so we denoted them with a $c$ subscript to show
they are dependent on the color ($R,B,Y$). 
\[
rad(\vec{V}_{triple}(n,c)) = max \{r_R, r_B, r_Y\}
\]
}

>>>>

A BC helix does not rest stably on a plane. It is convenient to
be able to ``untwist'' it and to form a tetrahelix space frame that has a
flat planar surface. By making length changes in a certain way, we can
untwist a tetrahelix to form a \emph{tetrabeam} which has planar faces
and has, for example, an equilateral triangular profile. This paper
develops the equations needed to untwist the tetrahelix. All math
developed here is available in JavaScript and demonstrated by an interactive
design website \url{https://pubinv.github.io/tetrahelix/}\cite{readtetrahelix}
\highlighttext{and a video\cite{readvideo}},
from which \cref{fig:closeup,fig:closeuporthog} and later figures in this paper 
are taken.

@@

Now that we have shown that axes are coincident and parallel and that the pitches
are the same for all helices, we can assert that any optimum tetrahelix can
be generated with an equation for helices:
\begin{equation}
\label{eq:triple}
\vec{V}_{triple}(n,c) =
\left [
  \begin{tabular}{c}
   $ r_c \cos(n \alpha +  c 2 \pi /3 + \phi_c)$\\
   $ r_c \sin(n \alpha +  c 2 \pi /3 + \phi_c) $\\
   $ \frac{d(n +c / 3)}{3}   $
  \end{tabular}
  \right ],
\end{equation}
\text{where: \qquad}
\begin{tabular}{l}
  $c \in \{0,1,2\}$,
  \end{tabular}      
which would be much more complicated if the axes where not coincident.
\highlighttext{
Having not yet investigated in the general case the relationships beteween
$\alpha$, $r$, $\phi$ and $d$ in \cref{eq:triple} for the three helices
which is developed in \cref{eqrhoopt} these are denoted with a $c$ subscript to show
they are dependent on the color ($c \in \{R,B,Y\}$). 
\[
rad(\vec{V}_{triple}(n,c)) = max \{r_R, r_B, r_Y\}
\]
}
